WORCS: A Workflow for Open Reproducible Code in Science

### 2020-11-02 paper/Manuscript_DS.Rmd
R1 C5 rmarkdown reference

Many researchers are motivated to adopt current best practices for open
science and enjoy these benefits. And yet, the question of how to 
get started can be daunting. Making the transition
requires researchers to become knowledgeable about different open science 
challenges and solutions, and to become proficient with new and unfamiliar tools.
This paper is designed to ease that transition by presenting a simple workflow 
that meets most requirements open science, and is based on best practices:
The *Workflow for Open Reproducible Code in Science* (WORCS).
WORCS is a lightweight approach to open science and
computational reproducibility for scholars working in `R` on a private computer,
conducting research that involves academic prose, analysis code,
and (optionally) tabular data - but it is flexible enough to accommodate many
other scenarios. The workflow (Figure 1) 
constitutes a step-by-step procedure that researchers can follow to make a 
research project open and reproducible.
WORCS is compatible with open science
requirements already implemented by journals and institutions, and will help 
fulfill them.
It can also be used to produce work in accordance with best practices
in the absence of top-down support or guidelines.
Although the principles underlying this workflow are universal, WORCS has been
implemented in `R` [@rcoreteamLanguageEnvironmentStatistical2020].
The `worcs` package [@worcs] offers a project template for RStudio
[@rstudioteamRStudioIntegratedDevelopment2015], which is, effectively,
a "one click solution". This paper discusses the principles underlying WORCS,
introduces the workflow, addresses how WORCS meets best practices for open science,
and illustrates the use of the `worcs` package.

@@

In the `R` implementation of WORCS, we recommend centering a research project
around one dynamically generated `RMarkdown` document, which includes all 
analysis code. Longer scripts can be
stored in `.R` files, and called from the main document using the `source()`
function. When a reader or reviewer compiles this document, all code is run
automatically, thus verifying computational replicability. The `RMarkdown` 
document can be automatically formatted in many styles, including
APA style [thanks to the `R` package `papaja`, @austPapajaPrepareReproducible2020],
a host of other scientific formats 
[see @allaireRticlesArticleFormats2020], and as plain `Markdown`.

>>>>

Many researchers are motivated to adopt current best practices for open
science and enjoy these benefits. And yet, the question of how to 
get started can be daunting. Making the transition
requires researchers to become knowledgeable about different open science 
challenges and solutions, and to become proficient with new and unfamiliar tools.
This paper is designed to ease that transition by presenting a simple workflow 
that meets most requirements open science, and is based on best practices:
The *Workflow for Open Reproducible Code in Science* (WORCS).
WORCS is a lightweight approach to open science and
computational reproducibility for scholars working in `R` on a private computer,
conducting research that involves academic prose, analysis code,
and (optionally) tabular data - but it is flexible enough to accommodate many
other scenarios. The workflow (Figure 1) 
constitutes a step-by-step procedure that researchers can follow to make a 
research project open and reproducible.
WORCS is compatible with open science
requirements already implemented by journals and institutions, and will help 
fulfill them.
It can also be used to produce work in accordance with best practices
in the absence of top-down support or guidelines.
Although the principles underlying this workflow are universal, WORCS has been
implemented in `R` [@rcoreteamLanguageEnvironmentStatistical2020].
The `worcs` package [@worcspackage2020] offers a project template for RStudio
[@rstudioteamRStudioIntegratedDevelopment2015], which is, effectively,
a "one click solution". This paper discusses the principles underlying WORCS,
introduces the workflow, addresses how WORCS meets best practices for open science,
and illustrates the use of the `worcs` package.

@@

In the `R` implementation of WORCS, we recommend centering a research project
around one dynamically generated `RMarkdown` document [@xieMarkdownDefinitiveGuide2018].
RMarkdown is based on [`Markdown`](https://en.wikipedia.org/wiki/Markdown),
which uses plain-text commands to typeset a document.
It enhances this format with support for R-code, and is compatible with [LaTeX](https://www.latex-project.org/) math typesetting.
For a full overview of the functionality of `RMarkdown`, see @xieMarkdownDefinitiveGuide2018.

The RMarkdown document can incorporate blocks of analysis code,
which can be used to render results directly to [Tables](https://bookdown.org/yihui/rmarkdown-cookbook/kable.html) and [Figures](http://zevross.com/blog/2017/06/19/tips-and-tricks-for-working-with-images-and-figures-in-r-markdown-documents/),
which can be [dynamically referenced](https://bookdown.org/yihui/rmarkdown-cookbook/cross-ref.html) in the text.
Long scripts can be stored in `.R` files,
and included in the main document using the [`read_chunk()`
function](https://github.com/yihui/knitr-examples/blob/master/113-externalization.Rmd) from the `knitr` package, which comes together with the `rmarkdown` package. When a reader or reviewer compiles this document, all code is run
automatically, thus verifying computational replicability. The `RMarkdown` 
document can be automatically formatted in many styles, including
APA style [thanks to the `R` package `papaja`, @austPapajaPrepareReproducible2020],
a host of other scientific formats 
[see @allaireRticlesArticleFormats2020], and as plain `Markdown`.

### 2020-11-02 paper/reviews_ds.Rmd
R1 C5 rmarkdown reference

\RC{I am confused by the citation "Van Lissa, Caspar J., Aaron Peikert, and Andreas M. Brandmaier. 2020. “Worcs: Workflow for Open Reproducible Code in Science.”". Is this referring to another paper or the actual package? If it's another paper then what is the contribution of this publication?}

@@

\RC{If the paper is generated as DDG, where are the functions that show it's capabilities? It is also not clear to me that some of the functionalities of Latex would be usable in RMarkdown, such as all the equations.}

Response: Add comment that LaTeX is supported in RMarkdown; showing functions (?) out of scope for present paper. Reference RMarkdown @xieMarkdownDefinitiveGuide2018

>>>>

\RC{C4: I am confused by the citation "Van Lissa, Caspar J., Aaron Peikert, and Andreas M. Brandmaier. 2020. “Worcs: Workflow for Open Reproducible Code in Science.”". Is this referring to another paper or the actual package? If it's another paper then what is the contribution of this publication?}

@@

\RC{C5: If the paper is generated as DDG, where are the functions that show it's capabilities? It is also not clear to me that some of the functionalities of Latex would be usable in RMarkdown, such as all the equations.}

Response: We understand that our introduction of the RMarkdown format was a bit too brief, and that readers may wonder whether specific functionalities of LaTeX would be usable in RMarkdown.
To address this comment, the revised manuscript now reads:

> In the `R` implementation of WORCS, we recommend centering a research project
around one dynamically generated `RMarkdown` document [@xieMarkdownDefinitiveGuide2018].
RMarkdown is based on [`Markdown`](https://en.wikipedia.org/wiki/Markdown),
which uses plain-text commands to typeset a document.
It enhances this format with support for R-code, and is compatible with [LaTeX](https://www.latex-project.org/) math typesetting.
For a full overview of the functionality of `RMarkdown`, see @xieMarkdownDefinitiveGuide2018.
